Push-Pull Signal-Function Functional Reactive Programming

### 2012-11-30 Docs/IFL2012/discussion.tex
IFL draft update
IFL paper draft update

The reactive algorithm is simple. A table from machine addresses to switch ports
is maintained. This table is updated in two ways. When a packet is sent to the
controller, meta-data for the packet indicates which port it arrived on. The
source address of the packet can then be mapped to that port in the table.
Once this occurs, rules are installed for each packet with a destination address
matching the source, along with reciprocal rules.

@@

\begin{figure}
\epsfig{file=graph.eps,angle=-90,width=\linewidth}
\hrule
\caption{Comparison of timeflies vs. Yampa implementing an OpenFlow learning switch controller.}
\label{fig:timeflies-yampa-comparison}
\end{figure}

There is some correlation between the sampling rate and the response rate
for TimeFlies, which is due to the continued wrapping of a replacement signal
function by {\tt switch} until the next time step (see Section~\ref{subsection:Implementation-Signal_Functions-Implementation_of_Signal_Function_Combinators}).
Nevertheless, TimeFlies outperforms Yampa in event response by several orders of magnitude,
even at a very high sampling rate. This is due to two factors. First, TimeFlies can react
to individual events without evaluating the whole signal function. Second, the
interface of time-flies permits us to connect its evaluation directly to GHC's event
manager, while the design of Yampa requires us to use threads and synchronized
communication\footnote{Yampa does include a step-wise evaluation function, but
it still couples event evaluation firmly to time steps, and is not well
documented.}.

>>>>

The reactive algorithm maintains a table of machine addresses to switch ports.
This table is updated in two ways. When a packet is sent to the controller,
meta-data for the packet indicates which port it arrived on. The source address
of the packet can then be mapped to that port in the table. Once this occurs,
rules are installed for each packet with a destination address matching the
source, along with reciprocal rules.

@@

\begin{figure}
\includegraphics[width=0.7\linewidth,angle=-90]{graph}
\hrule
\caption{Comparison of TimeFlies vs. Yampa implementing an OpenFlow learning switch controller.}
\label{fig:timeflies-yampa-comparison}
\end{figure}

There is some correlation between the sampling rate and the response rate
for TimeFlies, which is due to the continued wrapping of a replacement signal
function by {\tt switch} until the next time step (see Section~\ref{subsection:Implementation-Signal_Functions}).
Nevertheless, TimeFlies outperforms Yampa in event response by several orders of magnitude,
even at a very high sampling rate. This is due to two factors. First, TimeFlies can react
to individual events without evaluating the whole signal function. Second, the
interface of time-flies permits us to connect its evaluation directly to GHC's event
manager, while the design of Yampa requires us to use threads and synchronized
communication\footnote{Yampa does include a step-wise evaluation function, but
it still couples event evaluation firmly to time steps, and is not well
documented.}.

### 2012-11-30 Docs/IFL2012/introduction.tex
IFL paper draft update

FRP {\em combines} behaviors and events through the use of {\em switching}, in which
a behavior (in classic FRP) or a signal function (in signal-function FRP) is
replaced by a new behavior or signal function carried by an event occurrence.

>>>>

FRP combines behaviors and events through the use of {\em switching}, in which
a behavior (in classic FRP) or a signal function (in signal-function FRP) is
replaced by a new behavior or signal function carried by an event occurrence.
